Material Methods

### 2020-04-17 doc/MatMeth.Rmd
starting to change matmethods outline

---
title: "Material Methods"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '5'
  word_document:
    toc: yes
    toc_depth: '5'
bibliography: refs_MatMeth.bib
---

```{r set.up, echo=FALSE}
#set wd
#load datafile

@@

**SC Length calq**

# Mouse Husbandry

@@

# Tissue Collection and Immunohistochemistry

Spermatocyte spreads were collected and perpared as described in [@peterson_2019] . The majority of mice used were between 5 and 12 weeks, (supplemental table). for DMC1 spreads we targeted juvinile male mice (X ages).

@@

# Image Processing

@@

The total SC per cell and single bivalent measures were generated using the approaches discribed in [@wang_2019_sc] and [@peterson_2019] respectively.

@@

Single bivalent features were measured both manual and with an automated image analysis software [@Peterson_2019]

@@

# Statisical Analysis

@@

@@

### Single bivalent charaecterization

@@

>>>>

---
title: ''
date: '`r Sys.Date()`'
output:
  word_document:
    toc: yes
    toc_depth: '5'
  pdf_document:
    toc: yes
    toc_depth: '5'
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
bibliography: refs_Main_Report.bib
---

#Material Methods Draft v1

```{r set.up, echo=FALSE, include=FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
library(raster)
library(lme4)
library(nlme)
library(RLRsim)
library(ggpubr)
library(reshape2)
#library(patchwork)

#set wd
#load datafile
load(file="~./MLH1repo/data/Results_setup_4.16.20.RData")

@@

## Mouse Husbandry

@@

## Tissue Collection and Immunohistochemistry

Spermatocyte spreads were collected and perpared as described in [@peterson2019] . The majority of mice used were between 5 and 12 weeks, (supplemental table). for DMC1 spreads we targeted juvinile male mice (X ages).

@@

## Image Processing

@@

The total SC per cell and single bivalent measures were generated using the approaches discribed in [@wang_2019_sc] and [@peterson2019] respectively.

@@

Single bivalent features were measured both manual and with an automated image analysis software [@peterson2019]

@@

## Statisical Analysis

@@

### Models

@@

## Single bivalent charaecterization

@@

**SC Length model**
